Software Citation Principles

### 2016-04-19 sc-principles/software-citation-principles.tex
added policy maker to funder use case, addressing issue #112
moving table 1 down slightly
added statement on credit system to address issue #131

The principles in this document should guide further development of software citation
mechanisms and systems, and the reader should be able to look at any particular example
of software citation and see if it meets the principles.

@@

14.\ Show how funded software has been used      & \textbullet & \textbullet &             &             &             &             &             & \textbullet &             &             &             & Funder \\

@@

Following these efforts, we expect that FORCE11 will start a new working group
with the goal of supporting potential implementers of the software citation
principles as well as developing potential metadata standards, following the model
of the FORCE11 Data Citation Working Group.

>>>>

The principles in this document should guide further development of software citation
mechanisms and systems, and the reader should be able to look at any particular example
of software citation and see if it meets the principles.
Please note that while we strive to offer practical guidelines that acknowledge the current incentive system of academic citation, a more modern system of assigning credit is sorely needed.
It is not that academic software needs a separate system from academic papers, but that the need for credit for application software underscores the need to overhaul the system of credit for all research products.

@@

14.\ Show how funded software has been used      & \textbullet & \textbullet &             &             &             &             &             & \textbullet &             &             &             & Funder, policy maker \\

@@

Following these efforts, we expect that FORCE11 will start a new working group
with the goal of supporting potential implementers of the software citation
principles as well as developing potential metadata standards, following the model
of the FORCE11 Data Citation Working Group.
Beyond the efforts of this new working group, additional efforts should be focused on updating the academic credit system that focuses solely on citation.
